Paper Figures and Text

### 2023-01-27 Fish Data Analysis/Paper_Figures.qmd
Moved around files

school_data <- school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(School_Speed < 7) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           group_by(Flow_Ablation_Darkness) %>%
                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area),
                                  Groups_Mean_Val = mean(Groups), Groups_SD_Val = sd(Groups)) %>%
                           ungroup()
```

@@

group_still <- ggplot(group_sum_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time with this Many Groups") +
    theme_light()+ 
    scale_fill_manual(values=c("#1553BE","#2B76C4","#4098CA","#55BACF","#6BDDD5","#80FFDB")) +
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          axis.title.y = element_text(size = 15))

>>>>

school_data <- school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           #filter(School_Speed < 7) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           group_by(Flow_Ablation_Darkness) %>%
                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area),
                                  Groups_Mean_Val = mean(Groups), Groups_SD_Val = sd(Groups)) %>%
                           ungroup()
```

@@

group_still <- ggplot(group_sum_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time with this Many Groups") +
    theme_light()+ 
    scale_fill_manual(values=c("#0031B8","#1553BE","#2B76C4","#4098CA","#55BACF","#6BDDD5","#80FFDB")) +
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          axis.title.y = element_text(size = 15))
